MSc Thesis

### 2023-01-20 manuscript/main.tex
added line numbers

\documentclass[12pt, letterpaper, ]{article}
\usepackage[style=authoryear, maxnames=2, maxbibnames=99]{biblatex}
\addbibresource{total_biblio.bib}
\addbibresource{datasets.bib}
\usepackage{caption}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{url}
\graphicspath{./images/}
\geometry{
        letterpaper,
        top = 1.27cm,
        bottom = 1.27cm,
        left = 2.54cm,
        right = 2.54cm,
        }
\title{MSc Thesis}
\author{Isaac Peetoom Heida}
\date{December 2022}
\doublespace

@@

\subsubsection{Plant Growth and Treatments}

@@

\subsubsection{Sample Harvest and Preparation}

@@

\subsubsection{Statistical Analysis}

@@

\subsubsection{Plant Growing Conditions}

@@

\subsubsection{Plant Harvest and Sample Preparation}

@@

\subsubsection{Sample Analysis}

@@

>>>>

\documentclass[12pt, letterpaper, ]{article}
\usepackage[style=authoryear, maxnames=2, maxbibnames=99]{biblatex}
\addbibresource{total_biblio.bib}
\addbibresource{datasets.bib}
\usepackage{caption}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{url}
\usepackage{lineno}
\linenumbers
\graphicspath{./images/}
\geometry{
        letterpaper,
        top = 1.27cm,
        bottom = 1.27cm,
        left = 2.54cm,
        right = 2.54cm,
        }
\title{MSc Thesis}
\author{Isaac Peetoom Heida}
\date{December 2022}
\doublespace

@@

\subsubsection{Plant growth and experimental treatments}

@@

\subsubsection{Sample harvest and preparation}

@@

\subsubsection{Statistical analysis}

@@

\subsubsection{Plant growing conditions}

@@

\subsubsection{Plant harvest and sample preparation}

@@

\subsubsection{Sample analysis}

@@

\subsubsection{Statistical analysis}

To perfrom the GWAS analysis, I followed the methodology and code published in Gaurav et al. \citedate{gaurav_population_2021}. For brevity, this methodology only describes the steps we took using the data generated from Gaurav et al. \citedate{gaurav_population_2021}. For full details on how they generated the sequence data and prepared the final data sets refer to their manuscript. Prior to the linear regression to assess genetic associations, we first tested our phenotypic data for block effects within sites. For each site, we tested a linear model to see if measured leaf silicon content was significantly associated with block. We tested the model $y \sim Block + Accession$. When we validated that block had a negligible effect ($p>0.1$), we reparameterized leaf silicon measurements at the site level. We converted the raw \%Si to be expressed as the number of standard deviations the sample deviated from the site mean of \%Si. I did this to eliminate a possible confounding effect of inter-site differences that might reduce the power of the GWAS linear regression.

As per Gaurav et al. \citedate{gaurav_population_2021}, to reduce the computational intensity of my analysis, I prefiltered the total $k$-mer matrix to remove $k$-mers with a low chance of being informative [word choice?].
